### 2016-03-30 pdocs/thesis/introduction.tex
literature references for pdocs

Physics engines cannot used in serious structural analysis but using structural analysis in physics engines is not rare.  
E.g. \cite{Obrien:1999:GMA} used finite element model to analyze crack initiation and propagation.
Already \cite{cg1988} used quite similar principles as in this work to handle plasticity.

>>>>

Physics engines cannot used in serious structural analysis but using structural analysis in physics engines is not rare.  
E.g. \cite{Obrien:1999:GMA} used finite element model to analyze crack initiation and propagation.

Already \cite{cg1988} used quite similar principles as in this work to handle plasticity and there are quite a few further
papers that cite \cite{cg1988}. E.g. following papers provide alternative solutions to similar kind of simulations as 
are handled in this work 
\begin{itemize}
\item \cite{gibson1997survey} presents quite extensive study on deformable modelling in computer graphics
\item \cite{o2002graphical} provides excellent paper on ductile behaviour of material
\item \cite{muller2004point} presents a method for modeling and animating of 
elastic and plastic objects in realtime using point based animation
\item \cite{irving2004invertible} introduces algortithm for  finite element simulation of elastoplastic solids with very 
large deformations in reasonable time 
\end{itemize}
